Multiple Linear Regression on Sleep Data

### 2025-05-05 paper/paper.qmd
outlier add

```{r}
# Fit the model
full_model <- lm(sleep_duration ~ ., data = sleep)

# Get summary
model_summary <- summary(full_model)

@@

As far as assumptions go heteroskadcity seems to be true and normality might be slightly violated with heavy tails but their is no excessive deviation from normality.

```{r}
# Extract model diagnostics
model_data <- augment(full_model)

# Residuals vs Fitted plot
p5 <- ggplot(model_data, aes(.fitted, .resid)) +
  geom_point(size = 1) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  theme_few() +
  labs(title = "Residuals vs Fitted",
       x = "Fitted values", y = "Residuals")

# Q-Q plot
p6 <- ggplot(model_data, aes(sample = .resid)) +
  stat_qq(size = 1) +
  stat_qq_line() +
  theme_few() +
  labs(title = "Normal Q-Q Plot", x = "Theoretical Quantiles", y = "Sample Quantiles")

# Combine with patchwork
p5 / p6
```

>>>>

```{r}
full_model <- lm(sleep_duration ~ ., data = sleep)

model_summary <- summary(full_model)

@@

```{r}
model_data <- augment(full_model)

p5 <- ggplot(model_data, aes(.fitted, .resid)) +
  geom_point(size = 1) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  theme_few() +
  labs(title = "Residuals vs Fitted",
       x = "Fitted values", y = "Residuals")

p6 <- ggplot(model_data, aes(sample = .resid)) +
  stat_qq(size = 1) +
  stat_qq_line() +
  theme_few() +
  labs(title = "Normal Q-Q Plot", x = "Theoretical Quantiles", y = "Sample Quantiles")

p5 / p6
```

As far as assumptions go heteroskadcity seems to be true and normality might be slightly violated with heavy tails but there is no excessive deviation from normality.

Looking now towards outliers we selected observations that had one of following: leverage $> 2\cdot\frac{p+1}{n}$, studentized residual > 2, and a cooks threshold > 1. We saw
